Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-20 Manuscript/FLPhish(Trans).tex
调整位置

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the online shopping app users' purchase record data, patients' clinical data and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from consumers anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

>>>>

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.
